---
title: "assignment_5"
author: "Michael Stein"
date: "2025-10-03"
format: gfm
engine: knitr 
---

```{r}
library(tidyverse)
library(knitr)
library(gapminder)
library(dplyr)
```

## **Exercise 1. Trends in land value**

This excercise uses a dataset that describes the trends in land value (`Land.Value`), among other variables, in different states in the US 1975-2013. The states are grouped into four different regions, under the variable `region`. This dataset was obtained from the Data Science Services of Harvard University.

```{r}
housing <- read_csv("https://raw.githubusercontent.com/nt246/NTRES-6100-data-science/master/datasets/landdata_states.csv")
housing |> 
  head() |>  
  kable()
```

## **1.1 Washington DC was not assigned to a region in this dataset. According to the United States Census Bureau, however, DC is part of the South region. Here:**

-   Change the region of DC to “South” (Hint: there are multiple ways to do this, but mutate() and ifelse() might be helpful)
-   Create a new tibble or regular dataframe consisting of this new updated region variable along with the original variables State, Date and Land.Value (and no others)
-   Pull out the records from DC in this new data frame. How many records are there from DC? Show the first 6 lines.

```{r}
housing1 <- housing |> 
  mutate(region = ifelse(State == "DC", "South", region))

housing1 |> 
  filter(State == "DC") |> 
  head(6) |> 
  kable()

```

Answer: 153

#### **1.2 Generate a tibble/dataframe that summarizes the mean land value of each region at each time point and show its first 6 lines.**

```{r}
housing1 |> 
  group_by(region, Date)
  summarize(mean_land_value = mean(Land.Value))
  select(region, Date, mean_land_value)
```
